Domain-Driven Generative Data Model for BigPetStore

### 2014-07-16 bdcloud_paper/latex/paper.tex
Add implementation text

\section{Overview of Model \& Simulations}

@@

\section{Implementation}
Prototype using Python

\subsection{Output Format}

In line with the goal of generating data for analytics, the final output represents minimal information.  Although the model and simulation incorporate many internal parameters and state variables, these are ignored in the final output.  The final output consists of a table of transaction items like so:

* Customer Name
* Customer Location
* Store Location
* Transaction Number
* Transaction Date/time
* Item details (string)
* Item cost

[show example output]

@@

\section{Availability}
GitHub, Apache license

@@

% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

\section{Overview of Models \& Simulations}

@@

\section{Implementation}
The models and simulations were implemented using Python. The source code is available on GitHub \textcolor{red}{reference} at \url{https://github.com/rnowling/bigpetstore-data-generator} under the Apache 2 license.

@@

@@

% no \IEEEPARstart
%This demo file is intended to serve as a ``starter file''
%for IEEE conference papers produced under \LaTeX\ using
%IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
%I wish you the best of success.

%\hfill mds

%\hfill January 11, 2007

@@

\bibitem{IEEEhowto:kopka}
%\subsection{Subsection Heading Here}
%Subsection text here.

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
